---
title: "Homework 6"
author: "Yi Hang Khor"
date: "4/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
library(ggrepel)
```


1. Import the data and clean appropriately. To read in the data, you can use `readxl::read_xlsx('fileNameHere', sheet='sheetNameHere')`. Required data are in the sheets `Best in show` and `Best in show full sheet`. Take extra care on the column names and the first few rows of the data frame after read in.

```{r}
dat <- readxl::read_xlsx("KIB - Best in Show (public).xlsx",sheet='Best in show')
datfull <- readxl::read_xlsx("KIB - Best in Show (public).xlsx",sheet='Best in show full sheet')
```

Create a graphics similar to the top dogs figure. Your figure needs to display the following information with appropriate plotting elements:

```{r}
dogs <- datfull %>% select(1,3,32,5,6,11)
dogs <-dogs[-(1:3),]
names(dogs)<-c("breed","type","size","score","popularity","intelligence")
dogs$score <- as.numeric(dogs$score)
dogs$popularity <- as.numeric(dogs$popularity)
dogs$intelligence <- as.numeric(dogs$intelligence)
dogs$size <- as.factor(dogs$size)
dogs$size <- fct_rev(dogs$size)
dogs$type <- as.factor(dogs$type)
dogs <- dogs %>% mutate (intelligence = ifelse(intelligence >=40,"clever","dumb"))
dogs$intelligence <- as.factor(dogs$intelligence)  
dogs$intelligence <- fct_rev(dogs$intelligence)
dogsfinal <- na.omit(dogs)
str(dogsfinal)
```
```{r}
p <-ggplot(dogsfinal,aes(x = score ,y = popularity,color = type,label = breed,shape = intelligence,size =size))+ geom_point(alpha =.75)+
  scale_y_reverse()+ geom_vline(xintercept = 2.375) + geom_hline(yintercept = 87.5) +
  guides(label = FALSE)+ ggtitle("Best in Show: The Ultimate Data Dog")+
  theme(axis.text.x = element_blank(),axis.ticks.x = element_blank())+
  theme(axis.text.y = element_blank(),axis.ticks.y = element_blank()) +geom_text_repel(size=2,segment.size = 0.2)+
  theme_void()
p<- p+ annotate("text", label = "Inexplicably Overrated", x = 1.3, y = -5, size = 4)+
  annotate("text", label = "Hot Dogs!", x = 3.5, y = -5, size = 4) + 
  annotate("text", label = "The Rightly Ignored", x = 1.3, y = 172, size = 4) + 
  annotate("text", label = "Overlooked Treasures", x = 3.25, y = 172, size = 4) + 
  annotate("text", label = "Popularity", x = 2.4, y = -3, size = 4)+
  annotate("text", label = "our data score", x = 1.3, y = 86, size = 4)
p
```
